\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-28 paper.tex
add conclusion

\section{Conclusion}
\label{sec:conclusion}

>>>>

\section{Conclusion and Future Work}
\label{sec:conclusionAndFutureWork}

Despite the numerous pivots this project went through, in the end we were able
to create a useful working prototype. The Editour is fully featured with
everything needed to build an audio tour anywhere in the world. ARuko allows
users to experience useful AR-enhanced tours in a pleasant and intuitive way.
Together they provide a complete platform for building augmented reality tour
guide apps.

Although the finished product works as intended, we encountered several issues
along the way. The changing scope and goal of the project meant we spent several
weeks researching and working on features that did not make it into the final
product (see Section~\ref{sec:pivots}), such as displaying images in 3D AR space
and playing spatialized audio. If we had focused only on the features that made
it into the final app from the start we could have had more time to polish and
refine those features.

Another challenge we faced was the difficulty in actually testing the app. The
Ritsumeikan University Biwako-Kusatsu campus we stayed at is about ninety
minutes away from Kinkaku-ji by expensive public transport, which meant that we
were only able to go to the site to test ARuko twice. We could test some basic
features from Ritsumeikan, but image recognition target existed only at
Kinkaku-ji. More extensive user testing at the actual site could have helped us
catch bugs earlier and lead to a more polished final product.

Despite these issues our team is happy with the product we delivered to Kyoto
VR. ARuko is not quite ready to be sold on app stores yet, but with a little
more development time it could easily be made ready. The UI could use more
testing with real users to make sure it is intuitive and easy to use. We also
intended to add a feature where the app could automatically download tour files
from the Editour server and import them without having to rebuild. We were not
able to complete this feature due to time constraints, but it could easily be
added because all of ARuko's business logic is abstracted and generalized to
support multiple tours. Editour also already supports requesting and downloading
the most recent versions of tours.

Editour is essentially feature complete. The most recent version, v1.3.0, can be
found in the GitHub repository
(\url{https://github.com/bandaloo/editour/releases/tag/v1.3.0}), and it contains
all the features necessary to create and edit tours. In the future Kyoto VR
should move it to a more powerful hosting provider (see
Section~\ref{sec:deployingTheEditourBackend}), but the current solution works
for now.

Given more time and resources, the app should be augmented to include a tour
browser that automatically downloads an unpacks tours from the Editour server.
More historic locations around Kyoto and Japan in general should be considered
for other tours. With the work our team has done Kyoto VR now has a complete
platform for creating and delivering unique tours, which can easily be expanded
upon in the future.
